\documentclass{article}

\usepackage{indentfirst}

\begin{document}

\title{Resume}
\author{Zhe Zhang}

\maketitle

\newpage

\section*{Profile}

Name: Zhe Zhang

Birthday: 2/18/1981

Mobile: 13439993984

Email: zhangjiji.master@gmail.com

\section*{Education}

Degree: Bachelor

Major: Computer Science

University: Beijing University of Technology

\section*{Experience}

\subsection*{Aug/2011 --- Now \quad Glu mobile}

Making ios games using cocos2d-x which is a 2d rendering engine.

Begin to learn objective-c, ios SDK relative developments and technologies. Frequently use git and github. Will learn some knowledge about computer graphics, cocos2d-iphone, GLKit, GLES2.0. Unfortunately, I got a lower use rate of Emacs, but begin to use XCode. Will use Emacs more as soon as I get enough familiar with Mac development.

\subsection*{Jul/2010 --- Jul/2011 \quad Netease 01 Studio}

Develop online webgame ``San Guo Tian Xia'' using Lua script.

Begin to learn Lua, {\TeX}, and begin to use Emacs frequently. Know and Think about and Focus on bwapi relative projects in my spare time. Begin to learn basic algorithm and mathematics. Learn from Compilers and abstract programming language properties. Begin to aware of FP programming and abstract algebra. Begin to use Mac OS X.

\subsection*{Aug/2008 --- Jun/2010 \quad Maggi}

Develop MMO semi ACT/ semi RPG game using BigWorld engine which is a network middleware.

Begin to develop games. Begin to learn to use Python script. Use Emacs frequently. Begin to learn and focus on game AI. Latter half of that time, I concentrated on developing NPC decesion making system using GOAP(Goal Oriental Action Planning).

\subsection*{Jan/2004 --- Aug/2008}

Participate in serveral projects in China Software.

Making typesetting system in Founder International.

During these time, I like learning Standard C++. More clear with STL and Boost.

\section*{Most Important Books For Me TOP10}

As section title, There are some books important to me or make me feel astonished. Value and rank is not relative to the order of the list.

``Ruminations on C++''

``C++ Common Knowledge''

``Modern C++ Desing''

``Inside the C++ Object Model''

``Concrete Mathematics 2/e''

``3D Math Primer''

``Elements of Programming''

``The {\TeX} book''

``Version Control with Git''

``CODE''

\section*{Other Reference}

Github Account: zhangjiji

Projects, gists, wikis, octopress blogs, As time Accumulate I believe it will get well and rich of contents.

\section*{Referrals}

Wish can partcipate in AIIDE Starcraft AI war

Make games by myself.

AI, Compilers, Computer Graphics, Mathematics, Algorithms. I am interested in all of them, wish a big promotion on them.

\end{document}
